RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
removed redundant 'get'
typo fix

Like NEXUS files, NeXML documents can also contain character data.  While
most researchers will be familiar with the use of character matrices in
NEXUS files as a container for molecular sequence (or morphological) data 
used to infer the phylogenetic tree, we find this ideal for character data used in
comparative methods popular in R. Methods to get extract character data
work much like those for the phylogenetic data:

@@

Returns a `data.frame` with columns as characters and rows as
taxa. Continuous and discrete characters are represented as seperate
blocks in NeXML files, but will be combined as seperate columns of a
single data frame by `get_characters()` if they correspond to the same
taxa. The `get_characters_list()` function will consistently recieve
a list of data frames corresponding to each character matrix block of
the NeXML.

>>>>

Like NEXUS files, NeXML documents can also contain character data.  While
most researchers will be familiar with the use of character matrices in
NEXUS files as a container for molecular sequence (or morphological) data 
used to infer the phylogenetic tree, we find this ideal for character data used in
comparative methods popular in R. Methods to extract character data
work much like those for the phylogenetic data:

@@

Returns a `data.frame` with columns as characters and rows as
taxa. Continuous and discrete characters are represented as seperate
blocks in NeXML files, but will be combined as seperate columns of a
single data frame by `get_characters()` if they correspond to the same
taxa. The `get_characters_list()` function will consistently receive
a list of data frames corresponding to each character matrix block of
the NeXML.
